---
title: "BRM Homework 2"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
\newpage

# Introduction 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
rm(list=ls())
```

```{r, include=FALSE}
getwd()
setwd("/Users/charlottekasper/Desktop/Business Research Methods/Homework 2")
```

```{r, include = FALSE}
library(readxl)
library(latexpdf)
library(tinytex)
library(tidyverse)
library(ggplot2)
library(stargazer)
library(data.table)
library(bookdown)
library(readxl)
library(dplyr)
library(openxlsx)
library(xlsx)
```

## Introduction
research question: Are Housing variables helpful to fill-in missing values in Total household gross income?

In the following, we will answer the research question whether or not housing variables are helpful to fill-in missing values in Total household gross income. 
The data used to discover this question is public microdata for the European Survey on Income and Living Conditions (EU-SILC). 
(missing: brief overview of things we will be covering in this analysis)



## Variable Overview: 

HB010 - Year of the survey
HB020 - Country
HB030 - Household ID # use to join data from h and d
HB050 - Month of household interview # delete?
HB060 - Year of household interview # delete?
HB100 - Number of minutes to complete the household questionnaire # delete?

HY010 - Total household gross income # only consider values > 0
HY020 - Total disposable household income
HY022 - # Long name and not important?
HY023 - # Long name and not important?

# Housing variables - only use selected ones

HH010 - Dwelling type
HH021 - Tenure status
HH030 - Number of rooms
HH031 - Year of contract or purchasing or installation
HH040 - Leaking roof, damp wall/floors/foundation, or rot in window frames or floor
HH050 - Ability to keep home adequately warm
HH060 - Current rent related to occupied dwelling
HH061 - Subjective rent
HH070 - Total housing cost # only consider values > 0
HH71 - Mortgage principal repayment
HH081 - Bath or shower in dwelling
HH091 - Indoor flushing toilet for sole use of household

DB010 - Year of the survey
DB020 - Country
DB030 - Household ID # use to join data from h and d
DB080 - Household design weight # does not appear in data table (from reading weighting explanation)
DB090 - weight variable # use in the linear model fitting


Variables below are from reading the weighting explanation:

PB040 - Personal cross-sectional weight
PB060 - Personal cross-sectional weight for selected respondent
PB070 - Personal design weight for selected respondent

RB050 - Personal cross-sectional weight



```{r, include = FALSE}
Data_h <- read_excel("Mappe1.xlsx", 
    sheet = "h -household data")
Data_d <- read_excel("Mappe1.xlsx", 
    sheet = "d - household register")
View(Data_h)
names(Data_h)
```


```{r}
sheetH <- read.xlsx(
  "Mappe1.xlsx",
  sheet = "h -household data",
  )

sheetD <- read.xlsx(
  "Mappe1.xlsx",
  sheet = "d - household register",
  )

# Override sheet to filter the columns needed. sheet[rows (leave blank for all), c(columns to filter, separated by comma)]
sheetH = sheetH[, c(1,4,5,7)]
sheetD = sheetD[, c(2)]
sheet = data.frame(sheetH, sheetD)

View(sheet)
```




```{r}
summary(Data_h)
```

```{r}
datatable_h <- data.table(Data_h)
datatable_d <- data.table(Data_d)
```


## Dispose of observations where total gross income or total housing cost equals zero


```{r}
any(is.na(Data_h))
```
This functions gives us evidence about the question if we have zero values in the data (Problem: right now it searches in the whole table but we only want to check this for specific rows)

```{r}
na.omit(Data_h)
```
entfernt Reihen mit missing values. (Bezieht sich auf NA nicht auf 0...)

```{r}
mis2(, complete.cases(Data_h))
```
sollte eigentlich Spalten mit fehlenden Werten entfernen...

```{r}
select(iris, contains("0"))

```
150 Zeilen enthalten den Wert 0 

https://rstudio.com/wp-content/uploads/2015/06/data-wrangling-german.pdf

## create a datatable to work with 
extract the weight variable DB090 and used it in the linear model fitting (you can see how to use weights in function lm() using its help information)

## plotting Total household gross income

```{r, fig.width= 5, fig.height=3}
ggplot(data = Data_h, aes(x=HY010, y=HH070)) +
  geom_line() + 
  geom_point() +
  labs(x="HY010", y="Total housing cost", subtitle="xxx") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(breaks = seq(1960,2014, by=10))

```

Gegen was wollen wir Total gross income plotten? was soll auf die zweite achse?

```{r}
qplot(data = datatable_h, x = HY010, geom = "histogram") + theme_bw()
```
funktioniert nicht wegen discrete variable?

## weighting 
extract the weight variable DB090 and used it in the linear model fitting (you can see how to use weights in function lm() using its help information);

## Multiple Regression Ananlysis

# creating the lm function
```{r}
lm.spend1 <- lm(Total gross Income (HY010) ~ location + salary + children + catalogs,data = dt.marketing)
stargazer(lm.spend1, type = "text", no.space = TRUE)
```
anpassen!

#second model with other variables and a comparison table
```{r}
lm.spend2 <- lm(amountspent ~ location + salary + children + catalogs + history,
                data = dt.marketing)
stargazer(lm.spend1, lm.spend2, type = "text", no.space = TRUE)
```


## Comparison of the different regression models


## prediction model
Are you able to predict the Total household gross income (HY010) using only the housing variables?


```{r}
Total Gross income  <- data.table(HH012 = "Male",
                         location = "Close",
                         salary = 53700,
                         children = 1,
                         catalogs = 12)
```
anpassen an unsere Variablen die wir nehmen möchten

```{r}
my.pred <- predict(lm.spend1, newdata = new.client, level = .95, interval = "confidence")
my.pred
```
anpassen an unsere Variablen die wir nehmen möchten



